Visualisations for FEM IJM paper 1

### 2020-11-08 FEM_R/IJM_paper1_vis_WIP.Rmd
Added chunk for visualising the ReduceBMI intervention for testing

>>>>

# REDUCE BMI Intervention

base <- read_dta('ELSA_Baseline/ELSA_Baseline_summary.dta')
cohort <- read_dta('ELSA_cohort/ELSA_cohort_summary.dta')
pop_rbmi <- read_dta('ELSA_pop_BMI_reduc_obese/ELSA_pop_BMI_reduc_obese_summary.dta')
coh_rbmi <- read_dta('ELSA_coh_BMI_reduc_obese/ELSA_coh_BMI_reduc_obese_summary.dta')

ggplot(data = base, aes(x=year, y=a_bmi_all)) +
  geom_line()

ggplot(data = pop_rbmi, aes(x=year, y=a_bmi_all)) +
  geom_line()

ggplot(data=base, aes(x=year, y=p_cancre_all)) +
  geom_line()
ggplot(data=pop_rbmi, aes(x=year, y=p_cancre_all)) +
  geom_line()

ggplot(data=base, aes(x=year, y=p_diabe_all)) +
  geom_line()
ggplot(data=pop_rbmi, aes(x=year, y=p_diabe_all)) +
  geom_line()

ggplot(data=base, aes(x=year, y=p_hearte_all)) +
  geom_line()
ggplot(data=pop_rbmi, aes(x=year, y=p_hearte_all)) +
  geom_line()
